---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# githubr: An R Interface to GitHub

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/lwjohnst86/githubr.svg?branch=master)](https://travis-ci.org/lwjohnst86/githubr)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/lwjohnst86/githubr?branch=master&svg=true)](https://ci.appveyor.com/project/lwjohnst86/githubr)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)

The goal of githubr is to simplify using GitHub's API. Uses the wonderful [gh] R
package. Inspiration also comes from the [gitlabr].

[gh]: https://github.com/r-lib/gh
[gitlabr]: https://CRAN.R-project.org/package=gitlabr

## Installation

You can install the development version of githubr with:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("lwjohnst86/githubr")
```

## Examples

So far there are only functions to interact with Issues. For example, to list
issues or labels:

```{r}
library(githubr)

# See issues
gh_list_issues("lwjohnst86/carpenter")[[1]]

# See labels.
gh_list_labels("lwjohnst86/githubr")
```

## Contributing

Please note that the 'githubr' project is released with a [Contributor Code of
Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to
abide by its terms.
